---
title: "This is mine."
author: "Dirk Kayitare"
date: "6/24/2021"
output: html_document
bibliography: bibliography.bib
---

```{r, include=FALSE, echo = TRUE, eval = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = TRUE, 
               warning = FALSE, 
               message = FALSE, 
               error = TRUE)
```

```{r, echo = TRUE}
library(dplyr)
smoke <- c(TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, FALSE, TRUE, FALSE, FALSE, FALSE, FALSE, FALSE, FALSE, FALSE, FALSE, FALSE, TRUE, TRUE)
age <- c(35, 21, 20, 48, 20, 20, 22, 19, 19, 20, 19, 18, 24, 22, 22, 19, 21, 19, 21)
people <- data.frame(smoke, age)
people <- people %>%
  filter(age <= 34)
obs <- nrow(people)
```





# Intro

## Subheader

### Sub sub header

# Is smkong good for you?
Everyone knows smoking is no bueno.

# How many poeple smoke?
LOTS

Everyone knows that math is pretty easy [@Rudd2014].

Doctors prolly shouldn't sip on the liquor while on call [@Peterman2005]


# **Methods** 

My esteemed colleagues and I surveyed `r obs` people.

The average age of my participants is `r round(mean(age))` years. This is very _young_. **Right?**

# **Results**

The below chart shows the age of participants
```{r, echo = FALSE}
library(ggplot2)
ggplot(data = people,
       aes(x = age,
           y = smoke)) +
  geom_boxplot()
```


# Conclusion

Some people have smoked. Others have not. Fumar no bueno.

# Bibliography
